---
title: "Our title"
author: "Team XY"
date: "18th of November 2020"
output: 
  beamer_presentation
---

```{r setup, include=FALSE}
# SEE MORE: https://bookdown.org/yihui/rmarkdown-cookbook/
#           https://rmarkdown.rstudio.com/formats.html
# Presentations: https://bookdown.org/yihui/rmarkdown/beamer-presentation.html
knitr::opts_chunk$set(echo = FALSE, fig.asp = 0.8, fig.width = 7, out.width = "90%" )
```

## Our Question

- Introduction of the data

  - Outcome variable: 
  - Explanatory variable:
  - Potential data cleaning (1-2 bullet points)

Our question is:
  "HERE COMES YOUR RESEARCH QUESTION!"

```{r, include=FALSE}
# Clear memory
rm(list=ls())

# Packages to use
library(tidyverse)
# For scaling ggplots
require(scales)
# Estimate piecewise linear splines
#install.packages("lspline")
library(lspline)
# Estimate robust SE
#install.packages("estimatr")
library(estimatr)
# Compare models with robust SE
#install.packages("texreg")
library(texreg)
# For different themes
#install.packages(ggthemes)
library(ggthemes)

# Call the data from github
my_url <- "https://raw.githubusercontent.com/CEU-Economics-and-Business/ECBS-5208-Coding-1-Business-Analytics/master/Class_8/data/clean/WDI_lifeexp_clean.csv"
df <- read_csv( my_url )

df <- df %>% mutate( ln_gdppc = log( gdppc ) ,
                     ln_gdppc_sq = ln_gdppc^2 )

```


## Pattern of association - show your favorite model 
```{r , message=FALSE}
ggplot( data = df, aes( x = ln_gdppc, y = lifeexp ) ) + 
  geom_point( color='blue') +
  geom_smooth( method = lm , color = 'red' , formula = y ~ x)+
  labs(x = "ln( GDP/capita, 2018 int. const. $, PPP)",y = "Life expectancy  (years)")
```


## Model results

```{r, echo=FALSE, message=FALSE, results='asis'}

# Estimated regression models - ONLY INTERESTING ONES!!
# Simple
reg4 <- lm_robust( lifeexp ~ ln_gdppc , data = df )
# Quadratic
reg5 <- lm_robust( lifeexp ~ ln_gdppc + ln_gdppc_sq , data = df )
# Piecewise Linear Spline
cutoff_ln <- log( 50 )
reg6 <- lm_robust(lifeexp ~ lspline( ln_gdppc , cutoff_ln ), data = df )
# Weighted OLS
reg7 <- lm_robust(lifeexp ~ ln_gdppc, data = df , weights = population)

# print -!! IF NOT GOOD FIT TO SLIDE CHANGE FONTSIZE 
#     ("tiny", "scriptsize", "footnotesize", "small", "normalsize", "large", 
#       "Large", "LARGE", "huge", and "Huge") !!
# Alternatively may use 'scalebox = 0.5' but sometimes it breaks down...
texreg( list(reg4 , reg5 , reg6 , reg7),
         type = 'html',
         custom.model.names = c("Linear","Quadratic","P.L.S","WOLS"),
         custom.coef.names = c("Intercept","ln(GDP/capita)","ln(GDP/capita)^2",
                               "ln(GDP/capita<=50)","ln(GDP/capita>50)"),
         caption = 'Life expectancy and ln of GDP per capita models',
         include.ci = FALSE, include.rmse = FALSE,include.adjrs = FALSE,
         fontsize = 'small' )

```

## Test and Residuals

```{r , include=FALSE }

# Get the predicted y values from the model
df$reg4_y_pred <- reg4$fitted.values
# Calculate the errors of the model
df$reg4_res <- df$lifeexp - df$reg4_y_pred 

# Find country with largest negative errors
l1 <- df %>% top_n( -1 , reg4_res ) %>% 
      select( country , lifeexp , reg4_y_pred , reg4_res )

# Find country with largest positive errors
u1 <- df %>% top_n( 1 , reg4_res ) %>% 
       select( country , lifeexp , reg4_y_pred , reg4_res )

```

- We are interested in $H_0: \beta = 0, \, H_A: \beta \neq 0$ or not in our model. 
  - The estimated t-statistics is `r round(reg4$statistic[2],2)`, with p-value: `r reg4$p.value[2]`. 
  - Thus we reject the $H_0$, which means the life expectancy is not uncorrelated with GDP per capita. (OR you can interpret differently...)

- We investigated the residuals:
  - The largest negative deviance from the predicted value is found in `r l1[[1,1]]` with predicted life expectancy of `r round(l1[[1,3]],1)`, but the real value is only `r round(l1[[1,2]],1)`.
  - The largest positive deviance from the predicted value is found in `r u1[[1,1]]` with predicted life expectancy of `r round(u1[[1,3]],1)`, but the real value is `r round(u1[[1,2]],1)`.

## +1 Prediction

- What you predicted?
  - Statistical inference: 
    - CI of your predicted value
    - PI of your predicted value
  - External validity
    - What do you think? Would you trust your prediction? Time/Space/Group?

## Conclusion

- We investigated ... 
- and we have found
  - X and Y are ... correlated
  
- Our analysis can be 
  - strengthened by...
  - weakened by...
          



