---
title: "Daily Returns of Amazon Stock"
output:
  #pdf_document
  #html_document
  beamer_presentation
---

```{r setup, include=FALSE}
# Loading the packeges
library(tidyverse)
library(moments)
# Set the geral size of figures
knitr::opts_chunk$set(fig.width=3, fig.height=2) 
```

## Amazon Stock prices

As a shareholder in Amazon, the daily returns of Amazon's stock stands in the center of interest.

*Other interesting properties of Amazon stock prices.*

```{r }
# We can write codes easily

# Tidy approach: modify your path
data_in <- "/Users/agostonreguly/Dropbox/data/"

# Loading data
AMZN <- read.csv(paste0(data_in,"AMZN-KO1.csv"))

# Convert Date variable from string to date
AMZN$days <- as.Date(AMZN$Date,format = "%d/%m/%Y")
```

## Visualization

You can also embed plots in your report. Left graph shows the stock prices from 2005 until 2014. The right graph shows the distribution of daily returns.

```{r , echo=FALSE}
# Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.

# Time-series plot of stock prices
ggplot( data = AMZN , aes( x = days , y = Amzn_Close ) ) +
  geom_line( color = "red") +
  labs(x="Year (2005-2014)",y="Amazon Stock Value ($)") 

# Distribution of daily stock returns
ggplot( data = AMZN , aes( x = AMZN_Return ) ) + 
  geom_histogram( binwidth = 1 , fill = "navyblue" )+
  labs(x="Amazon Stock Daily Returns ($)",y="Count") 
```

The mean of the daily returns between 2005-2014 was `r mean(AMZN$AMZN_Return)`

## Summary statistics

Finally we can report the descriptive statistics 

```{r, echo=FALSE, results = 'asis'}
library(xtable)
options(xtable.comment = FALSE,include.rownames=FALSE)
# Create summary statistics for the distribution of the returns
amzn_sum_stat <- AMZN %>% summarise( mean     = mean(AMZN_Return),
                                     median   = median(AMZN_Return),
                                     std      = sd(AMZN_Return),
                                     iq_range = IQR(AMZN_Return), 
                                     min      = min(AMZN_Return),
                                     max      = max(AMZN_Return),
                                     skew     = skewness(AMZN_Return),
                                     numObs   = n() )
# Create good looking table
xtable(amzn_sum_stat)

```


## Conclusion

Rmarkdown is a great tool to create reports! Rmarkdown shines in two cases: 
1. when you want to share the whole report and also check how it was down (e.g. controlling) 
2. when you create periodical reports and you need to refresh the data

However if you only need to create a single report you might consider the effectiveness of its use.



