---
title: "My analysis"
date: 2020-10-12
author: "Team XY"
output: pdf_document
        #html_document
  
---

## This is a section name

Here you can easily write any text or you can reference your [github repo](https://github.com/CEU-Economics-and-Business/ECBS-5208-Coding-1-Business-Analytics) or your favorite site <https://github.com>.

You can highlight your text using **Bold** values or *italics*. Or you can create unordered lists:

* My first item
  + My first sub item
    - sub-sub item
* My second item, ect.

@. Ordered list
@. This  continues the ordered list

## You can use it as a script

```{r , include = FALSE}
library(tidyverse)
data_in <- "~/Documents/Egyetem/CEU/Teaching_2020/Coding_with_R/git_coding_1/ECBS-5208-Coding-1-Business-Analytics/Class_2/data/"
hv <- read_csv( paste0(data_in,"clean/hotels_vienna.csv") )
```

Then you will not see anything...

## Or you can include your scripts as well
```{ r }
summary(hv$price)
```

## Or include only the output of your scripts
```{r , echo = FALSE }
summary(hv$price)
```

## Including Plots

You can also embed plots, for example:

```{r, echo=FALSE}
ggplot( data = hv , aes( x = price ) ) +
  geom_histogram( aes(y = ..density..) , fill = 'navyblue' , binwidth = 15 ) +
  geom_density( aes(y = ..density..) , fill = 'red' , bw = 15, alpha = 0.5 ) +
  labs(x='Hotel Prices in Vienna',y='Density')+
  scale_y_continuous(labels = scales::percent)
```

## Different size of plots
```{r, echo=FALSE, out.width = '50%' }
ggplot( data = hv , aes( x = price ) ) +
  geom_histogram( aes(y = ..density..) , fill = 'navyblue' , binwidth = 15 ) +
  labs(x='Hotel Prices in Vienna',y='Density')+
  scale_y_continuous(labels = scales::percent)

ggplot( data = hv , aes( x = price ) ) +
  geom_density( aes(y = ..density..) , fill = 'red' , bw = 15, alpha = 0.5 ) +
  labs(x='Hotel Prices in Vienna',y='Density')+
  scale_y_continuous(labels = scales::percent)
```

## Including Tables

You can also embed tables, for example:

```{r, echo = FALSE }
library(moments)

vienna_sum_stat <- hv %>% summarise(
  mean     = mean(price),
  median   = median(price),
  std      = sd(price),
  iq_range = IQR(price), 
  min      = min(price),
  max      = max(price),
  skew     = skewness(price),
  numObs   = n() )

knitr::kable(vienna_sum_stat,caption="Summary stat for hotel prices")

```

## Or you shall use a bit more sophisticated package
```{r, echo = FALSE , results = "asis", warning = FALSE, message = FALSE }
#install.package("xtable")
library(xtable)

xtb <- xtable(vienna_sum_stat,type = "latex", caption = "Summary statistics - better package")
print(xtb, comment=FALSE, include.rownames=FALSE)

```

# Summary of your resutls

Here you summarize your results and you may include some code as well `r round(mean(hv$price),2)` in line.

## Further information on Rmarkdown
R for data science Chapter 21 full and 23 first part (until page 475)

## Chapters for cleaning and filtering with tibble
R for data science Chapter 3 (until p 71) and 7